Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-05-10 tex/VHzQ.tex
VHzQ.tex polish

Tables~\ref{tab:THE_TABLE}, \ref{tab:THE_TABLE_NIR} and~\ref{tab:THE_TABLE_MIR}, represent the culmination of this effort, and we now describe the assembly of their contents in more detail.

@@

     There are 14 objects that have no NIR detections. 
     3 of these (PSOJ053.9605-15.7956, PSO J056.7168-16.4769, DELSJ0411-0907) 
     have been observed, but are out of our queried time range. 
     6 objects have not been observed (or at least the data is not in the WSA/VSA 
     archives yet) and 5 objects at $\geq +60$ deg$^{2}$ are too far north for UKIRT 
     and cannot be observed.

>>>>

Tables~\ref{tab:WSA_wWISE}, \ref{tab:THE_TABLE_NIR} and~\ref{tab:THE_TABLE_MIR}, represent the culmination of this effort, and we now describe the assembly of their contents in more detail.

\input{table_tex/WSA_wWISE}

@@

     There are 14 objects that have no NIR detections. 
     3 of these (PSOJ053.9605-15.7956, PSO J056.7168-16.4769 and DELSJ0411-0907) 
     have been observed (by VHS) but are out of our queried time range. 
     6 objects have not been observed (or at least the data is not in the WSA/VSA 
     archives yet) and 5 objects at $\geq +60$ deg$^{2}$ are too far north for UKIRT 
     and cannot be observed.
